Collate Rarefied Samples and Null Models

### 2021-10-13 analysis/04_collate_rarefied_null.Rmd
Add description at the top.
typo
Add in CWM for continuous variables.

@@

@@

Merge rarefied species and fd metrics and null models
```{r}
rarefied_metrics <- full_join(species_metrics, fd_metrics,
                              c("YEAR", "cell", "rarefy_resamp", "rarefyID")) %>%
  filter(S != 1) %>% # remove samples that had one species as they result in strange metric values
  select(-qual.FRic)

@@

##	calculate the medians for all the metrics for studies that were rarefied
metric_cols <- ungroup(rarefied_metrics) %>%
  select(-c(SamplePool, SampleN, num_years, duration, startYear, endYear, CWM, type)) %>%
  pivot_longer(-c(rarefyID, rarefied, YEAR, cell, rarefy_resamp), names_to = "metric") %>%
  left_join(null_table %>% select(-c(richness, se, lowerCI, upperCI)),
            by = c("YEAR" = "year", "rarefyID" = "rarefyid", "rarefy_resamp" = "rarefy_resamp", "metric" = "metric"))

>>>>

This script reads in all the rarefacation sample files, gets the median value for each rarefyID and year, and then merges with null model statistics.

@@

#read in CWM metrics
path <- here::here("data", "rarefied_metrics", "cwm")
filelist <-  dir(path, "*.rda") %>%
  paste0(path, "/", .)

cwm_metrics <- purrr::map_dfr(filelist, function(x) {
  load(x)
  rarefyID <- str_match(x,"_cell\\s*(.*?)\\s*_sample")[,2]

  if(dim(cwm_metrics)[1] == 0){
    return(data.frame())
  }else{

    cwm_metrics <- cwm_metrics$CWM %>%
      rownames_to_column("YEAR") %>%
      mutate(YEAR = as.integer(YEAR)) %>%
      left_join(cwm_metrics %>% select(-CWM)) %>%
      mutate(rarefyID = rarefyID)

    return(cwm_metrics)
  }
})

@@

Merge rarefied species and fd metrics and null models
```{r}
rarefied_metrics <- full_join(species_metrics, fd_metrics %>% select(-CWM),
                              c("YEAR", "cell", "rarefy_resamp", "rarefyID")) %>%
  full_join(cwm_metrics, c("YEAR", "cell", "rarefy_resamp", "rarefyID")) %>%
  filter(S != 1) %>% # remove samples that had one species as they result in strange metric values
  select(-qual.FRic)

@@

##	calculate the medians for all the metrics for studies that were rarefied
## exclude categorical variables - they don't make sense as medians
metric_cols <- ungroup(rarefied_metrics) %>%
  select(-c(SamplePool, SampleN, num_years, duration, startYear, endYear, type,
            diet_5cat, pelagicspecialist, diurnal, nocturnal, crepuscular, dir, lar)) %>%
  pivot_longer(-c(rarefyID, rarefied, YEAR, cell, rarefy_resamp), names_to = "metric") %>%
  left_join(null_table %>% select(-c(richness, se, lowerCI, upperCI)),
            by = c("YEAR" = "year", "rarefyID" = "rarefyid", "rarefy_resamp" = "rarefy_resamp", "metric" = "metric"))
